---
title: "KIN 377 - Web Exercises"
format: 
  html:
    css: [webex.css]
    include-after-body: [webex.js]
    embed-resources: true 
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(webexercises)
```

```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple", highlight = "firebrick")
```

Students can test their knowledge by answering the questions below after reviewing each chapter.

# Chapter 11 {#sec-chapter-11}

::: {.webex-check .webex-box}
1.  A retention test typically follows a period after the practice of a skill has ceased. `r torf(TRUE)`
2.  An important performance characteristic associated with learning is that the person becomes increasingly more capable of adapting the performance of the skill to new performance contexts and situations. `r torf(TRUE)`

```{r, results='asis'}
opts <- c(
   "Learning",
   answer = "Performance",
   "Practice",
   "Skill"
)

cat("3. In the motor learning research literature, which term refers to _observable behavior_?", longmcq(opts))
```

```{r, results='asis'}
opts <- c(
   "can be directly observed",
   answer = "results in relatively permanent improvement",
   "can be observed during practice",
   "results in consistently correct performance"
)

cat("4. An essential component of the definition of learning is that it:", longmcq(opts))
```

```{r, results='asis'}
opts <- c(
   "increase",
   answer = "decrease",
   "not change",
   "be impossible to predict"
)

cat("5. As a person learns a new skill the attention demanded by the skill will:", longmcq(opts))
```
:::
